Workplan

### 2018-04-26 LiteratureReview/LiteratureReview.tex
continue to work on literature review and make amendments to other documents

\section{Introduction to Dementia and the Literature Review}
\par
Identification of language impairment is important in Dementia because it aids diagnosis of specific types of dementia, which in turn can alter the prognosis and change the management of the degenerative disorder. As these differences in language are quite subtle, the varying subtypes of dementia are frequently misdiagnosed.
\newline
\par
According to a recent report commissioned by the Alzheimer's Society, they estimate the prevalence of Dementia in the UK at approximately 815,000 people. This represents 1 in 14 of the population aged 65 or over. This report also estimates an annual healthcare spend on £4.3 billion of which approximately £85 million is spend solely on diagnosis. They also estimate that the overall impact of dementia (excluding the costs associated with early onset dementia) is £26.3 billion annually.
\newline
\par
The purpose of this review is to seek to understand how dementia impacts speech and language production from a clinical psychology perspective. This review goes on to

% Describe how you have conducted the search. What did you search, how did you search, how did you filter.

@@

\section{Conclusion}
Given the burden on the diagnosis of dementia on clinicians, it appears to be useful to find some non-invasive protocols for the early diagnosis of dementia. 
\end {document}

>>>>

\section{Introduction}

\par
According to a recent report commissioned by the Alzheimer's Society, they estimate the prevalence of Dementia in the UK at approximately 815,000 people. This represents 1 in 14 of the population aged 65 or over. This report also estimates an annual healthcare spend on £4.3 billion of which approximately £85 million is spend solely on diagnosis. They also estimate that the overall impact of dementia (excluding the costs associated with early onset dementia) is £26.3 billion annually. Globally, this picture is a lot bleaker. A recent report suggests that in 2015 there were 46 million people with a diagnosis of dementia and that number is expected to hit 131.5 million by 2050(CITE). The report also states that the worldwide cost of dementia in 2018 is estimated to be in the region of one trillon US dollars.
\newline
\par
The purpose of this review is to seek to understand how dementia impacts speech and language production from a psychological and linguistic perspective with a view to potentially using natural language processing and technology to aid in the early diagnosis of dementia and/or Mild Cognitive Impairment.
\newline
\par
A search of the literature was conducted mainly from a psychological perspective as this would inform the theoretical side of things. Next, a search of the literature from a Computer Science perspective was also made with a view to exploring the how domain of machine learning and more specifically natural language processing can be applied to this problem. Finally a search was carried out to see what work has already been done in this area.

All stages of this literature review were completed by myself.

@@

\section{Conclusion}
\par
Identification of language impairment is important in Dementia because it aids diagnosis of specific types of dementia, which in turn can alter the prognosis and change the management of the degenerative disorder. As these differences in language are quite subtle, the varying subtypes of dementia are frequently misdiagnosed.
\newline
\par 
Given the burden on the diagnosis of dementia on clinicians, it appears to be useful to find some non-invasive protocols for the early diagnosis of dementia. It has already been shown that analysis of speech and language has shown markers that pre-date the official diagnosis of dementia (Snowdon et al, 1996; Berisha et al, 2015).
\end {document}

### 2018-04-26 QualifyingReport/QualifyingReport.tex
updated structure on Literature Review
continue to work on literature review and make amendments to other documents

@@

	\section{Proposed Timetable}
	\subsection{May 2019}

@@

	\subsection{April 2021}
	\section{Provision Table of Contents}
\end{document}

>>>>

	\subsection{April 2018}

	Thursday, 26th April - Workplan (First Draft Agreed)

@@

	\section{Proposed Timetable}

	\subsection{May 2018}
	Wednesday, 9th May - Alexa Skills Training (All Day)
	\subsection{June 2018}
	Friday 15th June - First Draft of Literature Review to be handed in.
	\newline
	Monday 18th June - Monday 25th June - Annual Leave
	\subsection{July 2018}

	\subsection{August 2018}

	\subsection{September 2018}

	\subsection{October 2018}

	\subsection{November 2018}

	\subsection{December 2018}

	\subsection{January 2019}
	Friday 11th January - Rough Draft of Qualifying Due
	Friday 18th January - Complete first rough pass of capturing and processing speech.

	\subsection{February 2019}
	Friday, 1st February - Qualifying Report Due

	\subsection{March 2019}

	\subsection{April 2019}
	Monday, 1st April - Viva Due by this point.
	\subsection{May 2019}

@@

	\subsection{April 2021}
	\section{Provision Table of Contents}
	\subsection{Chapter 1: Introduction}
	\subsection{Chapter 2: Literature Review}
	\subsection{Chapter 3: New theories, Description of experiments}
	\subsection{Chapter 4: Results}
	\subsection{Chapter 5: Discussion}
	\subsection{Chapter 6: Conclusion}
\end{document}

### 2018-04-26 Workplan/Workplan.tex
continue to work on literature review and make amendments to other documents

	\section{Proposed Timeline, Key Dates and Deliverables}
	\subsection{April 2018}
	Wednesday, 18th April - Workplan (First Draft Agreed)
	\subsection{May 2018}
	Wednesday, 9th May - Alexa Skills Training (All Day)
	\subsection{June 2018}
	Friday 15th June - First Draft of Literature Review to be handed in.
	\newline
	Monday 18th June - Monday 25th June - Annual Leave
	\subsection{July 2018}

	\subsection{August 2018}

	\subsection{September 2018}

	\subsection{October 2018}

>>>>

	\section{Proposed Timeline, Key Dates and Deliverables}
	\subsection{April 2018}
	Thursday, 26th April - Workplan (First Draft Agreed)
	\subsection{May 2018}
	Wednesday, 9th May - Alexa Skills Training (All Day)
	\subsection{June 2018}
	Friday 15th June - First Draft of Literature Review to be handed in.
	\newline
	Monday 18th June - Monday 25th June - Annual Leave
	\subsection{July 2018}

	\subsection{August 2018}
	Friday 10th August - First draft of experimental proposal to be submitted.

	\subsection{September 2018}
	Friday 21st September - Final draft of experimental proposal to be submitted. 
	Friday 21st September - NHS Ethics forms to be sorted  - Takes 60 days!
	\subsection{October 2018}
